\documentclass[12pt]{article}
\usepackage[legalpaper, margin=0.5in]{geometry}
\usepackage{titlesec}

\titleformat{\subsection}
{}
{}
{}
{} [\titlerule]

\author{Tim Pasquel}

\title{CSC354 Software Engineering}

\begin{document}

\maketitle

\titlepage

\section{Jan Notes:}

\subsection*{Jan 24 2024}

\begin{itemize}
		  \item \textbf{Steps:} Define solution (Find the goal with the client), design, code  
		  \item Prototype the hardest thing 1st so you can fail fast 
		  \item \textbf{Optional Books:} \it{Peopleware: Productive Teams and Projects, 3rd Eidtion, Tom Demarco \& Tim Lister, Addison-Wesley}
\end{itemize}

\subsection*{Jan 26 2024}

\textbf{Project Ideas:}

More info can be found on Openai

\begin{enumerate}
		  \item Community Safety Network App
		  \item Personal Finance Coach (Similar to the Wii fit toaster) 
		  \item Waste Reduction Tracker
		  \item Plant Care and Identification 
		  \item DIY Home Improvement Assistant 
		  \item Speed test, but with system applications as variables 
		  \item Plant monitor with raspberry pi 
\end{enumerate}

\textbf{Good Idea:} Plant Monitor that uses a raspberry pi with a water sensor
\begin{itemize}
		  \item Use a pi zero 
		  \item use a pi water sensor found here: https://newbiely.com/tutorials/raspberry-pi/raspberry-pi-water-sensor
		  \item Create a python script that can read the water level data, help can be found on the website above 
		  \item Craete either a app or a webapp that can recive this information from the pi
		  \item Have the user create an account and then put in plant data
		  \item App will then read the plant needs and give the user notifications if the water level is too low
		  \item \textbf{Opt:} Have an automatic watering system if the water level gets too low
		  \item \textbf{Opt:} Figure out a way to have multiple of these devices running on one raspberry pi
		  \item Have a library on the app with common water levels for plants 
		  \item \textbf{Opt:} Have a chat board in which users can dicuss the best water options for plants 
\end{itemize}

\subsection*{Jan 29 2024}

Project Pitches

\begin{itemize}
		  \item \textbf{Edutainment:} Game, 5 People, typing game to teach kids about jobs 
		  \item \textbf{ghest:} Motion device that pairs with bluetooth devices (Play, audio, video, messaging)
		  \item \textbf{PlantPro:} Me :). Additions: How will I power it, more sensors
		  \item \textbf{Have a Hobby:} App. that helps people find hobbies that they enjoy, reddit like, for 
					 the local location (set a range).
		  \item \textbf{Camera Detection:} Pi device that Detects IR waves and display it to the user, similar
					 to a flipper zero
\end{itemize}

\subsection*{Jan 31 2024}

\begin{itemize}
		  \item Road Map: Scope, Planning, Requirements, Architecture, Prototype, Test Plan, Design, Sprints, Delivery
		  \item \textbf{Scope:} Determine whats \underline{inside} and \underline{outside} the system. 
					 \textbf{Artifacts:} Context diagram, user stories, use cases
		  \item \textbf{Planning:} Whats skills does the team \underline{have/need}. Who is responsible for what. 
					 \textbf{Artifacts:} Soft. Dev. Plan, PERT/Gantt Chart
		  \item \textbf{Requirements:} What are the \underline{functional} and \underline{non functional} 
					 requirements. User workflow? \textbf{Artifacts:} Software requirement specification
		  \item \textbf{Architecture:} Based on requirements, \underline{what servers} and \underline{hardware} are needed? 
					 Development environments? \textbf{Artifacts:} Architecture Diagram
		  \item \textbf{Planning pt2:} What is the \underline{highest risk} portion of the application? What do you understand
					 the least? \textbf{Artifacts:} Software Dev. Plan
		  \item \textbf{Prototype:} Design/build a working prototype. Research unknown items. Try different solutions. 
					 Create the prototype. \textbf{Artifacts:} Working prototype
		  \item \textbf{Test Plan:} Create system test plan based on \underline{user stories},
					 \underline{functional requirements}, \underline{non functional}
					 requirements. \textbf{Artifacts:} Test Plans
		  \item \textbf{Design:} Create a system level \underline{Class Diagram}. \textbf{Artifacts:} 
					 Detailed Design Specification
		  \item \textbf{Sprints:} Many sprints, each creates \underline{user functionality}. Each one is 2 weeks, goal is 4 total.
					 Sequence diagrams, code, test, deploy. \textbf{Artifact:} Detailed design specifaction
		  \item \textbf{Delivery:} Final user acceptance testing/report. How do you \underline{install} the system?
					 How do you \underline{use} the system? Demo day? \textbf{Artifacts:} Testing report, user manual, installation
					 guide.
\end{itemize}

\subsection*{Feb 2 2024}

Chapter 1: Creating a program

\begin{itemize}
		  \item We all ``start'' by learning how to code in 1 language in 1 module
		  \item Learn to \underline{test} the program
		  \item Learn to \underline{re-read} or \underline{re-think} the program/problem
		  \item Learn to \underline{trace} and  \underline{``debugging''} the program
		  \item Learn to figure out if it is \underline{``good enough''}
		  \item \textbf{\underline{Testing:}}
					 \begin{itemize}
								\item While the program is being defined
								\item While it is developed
								\item After its completed
					 \end{itemize}
		  \item \textbf{\underline{Kinds of Testing:}}
					 \begin{itemize}
								\item Acceptance (Validation) 
								\item Verification
								\item Unit testing
								\item Black box
								\item White box
					 \end{itemize}
		  \item \textbf{\underline{What else matters:}}
					 \begin{itemize}
								\item How long did it take to complete the work? 
								\item How much effort (total person hours)? 
										  Ex. 80hrs in 2 weeks, 64hrs (80\% of the time)
								\item Does it solve the problem?
								\item How good is it?
					 \end{itemize}
\end{itemize}

\subsection*{Feb 7 2024}

Chapter 1: Creating a program

\begin{itemize}
		  \item \textbf{\underline{Roadmap:}}
					 \begin{enumerate}
								\item Figure out the requirements 
								\item Draw the architecture
								\item Design the software/hardware
								\item Sprints, create working systems
								\item Deploy the projects
					 \end{enumerate}
		  \item \textbf{\underline{Project Data Storage:}}
					 \begin{itemize}
								\item Google Drive (Google can see, but you own it)
								\item One Drive (Kutztown sees and owns everything on it)
								\item Dropbox
					 \end{itemize}
		  \item \textbf{\underline{Project Drawings:}}
					 \begin{itemize}
								\item Draw.io
								\item Lucid Chart
					 \end{itemize}
		  \item \textbf{\underline{Ghantt Charts:}}
					 \begin{itemize}
								\item Git Hub
								\item Trello
					 \end{itemize}
\end{itemize}

\subsection*{Feb 9 2024}

\begin{itemize}
		  \item \textbf{UML:} Unified Modeling Language, a way to display object oriented projects
					 \begin{itemize}
		  				  		\item Ignore the irrelevant details (What language)
		  				  		\item Represent the relevant details (What data do we need, what interacts with what)
								\item Focus on the what not the how
					 \end{itemize}
		  \item \textbf{80-20 rule:} Pareto Principle (80\% of profits come from 20\% of customers, etc.)

\end{itemize}

\subsection*{Feb 12 2024}

\textbf{Scope Diagram}

\begin{itemize}
		  \item \textbf{UML Context Diagram:} Used during requirements elicitation and analysis
					 to negotiate what is inside or outside the system. 
		  \item \textbf{UML Actor:} A model for an external entity which interacts with the system. Ex
					 User, external system, phyiscal environment
		  \item \textbf{User Stories:} For each actor define how they interact with the system. Ex. Instructor
					 will give lecture, assign homework. Students will attend lectures, do the work. 
		  \item \textbf{Use Case Diagrams:} Represent the functionality of the system from the 
					 \underline{user's point of view} (7 +- 2, verb - noun). Use the User Stories to help
					 generate the High Level Use Cases
		  \item \textbf{Use Case Descriptions:} Use cases are described textually, with a focus 
					 on the event flow between actor and system.
					 \begin{enumerate}
								\item Unique name
								\item Participating actors
								\item Entry conditions
								\item Exit conditions
								\item Flow of events
								\item Special requirements
					 \end{enumerate}
		  \item \textbf{Example Gas Pump:}
					 \begin{enumerate}
								\item User Stories:
										  \begin{itemize}
													 \item \underline{Driver:} Pump gas, pay for gas, see cost of gas per 
																gallon,see total cost, choose between gas and disel and diffferent
																grades, park at the pump, have gas automatically turn off:
																when tank is full; or \$ reached, choose receipt, have 
																kill switch work.
													 \item \underline{Car:} Open gas tank, get the gas, nozzle fits,
																etc. 
										  \end{itemize}
								\item Use Cases:
										  \begin{itemize}
													 \item Choose gas type (Driver)
													 \item Pump gas (Driver)
													 \item Manage Payment (Clerk, Driver)
													 \item Kill switch (Clerk, Driver)
										  \end{itemize}
					 \end{enumerate}
\end{itemize}

\subsection*{Feb 14 2024}

\begin{itemize}
		  \item N/A 
\end{itemize}

\subsection*{Feb 21 2024}

Chapter 2

\begin{itemize}
		  \item \textbf{Decomposition:} Breaking down the problem and the solution
		  \item \textbf{Modularization:} Divide the solution into small parts
		  \item \textbf{Separation of Concerns:} Figure out what goes to each section
		  \item \textbf{Incrementally:} Resolve problems in chunks (sprints)
		  \item \textbf{Tools and Technologies:}
		  		\begin{itemize}
		  			\item Databases to handle information
		  			\item Development platforms for programmings
		  			\item Computing networks
		  			\item Configuration management for multi developers
		  			\item Modeling for problems and solutions
		  			\item Automated testing
		  		\end{itemize}
		  \item \textbf{Improve Process and Methodologies:}
		  		\begin{itemize}
					\item Coordinate multiple people for different tasks
					\item Guidance for overlapping incremental tasks
					\item Guidance for measuring separate artifacts and outcomes
		  		\end{itemize}
		  \item \textbf{Task breakdown:}
		  		\begin{enumerate}
					\item Who performas what task?
					\item How is that task completed, techniques or tools used?
					\item When should each task start and end?
					\item Who is coordinating the people and tasks?
		  		\end{enumerate}
		  \item \textbf{Iterative Process:}
		  		\begin{enumerate}
					\item Software Development Plant (SDP)
					\item Understanding the Broad Problem
					\item Architecture and High Level Design
					\item Specific Requirements
					\item Detail Design
					\item Code
					\item Software Integration
					\item Testing
		  		\end{enumerate}
			\item \textbf{Effort and Scheduling:} How long does this take to handle?
			\item \textbf{Assignment and Communiction:} More people more issues, 
					do we need some process, do we need some tools?
		  \item \textbf{Building Complex Systems:}
		  		\begin{itemize}
					\item \underline{Requirements:} Gathering, analysis, specification, agreement
					\item \underline{Design:} Abstraction, decomposition, interaction, coupling analysis
					\item \underline{Implementation:} Coding and unit testing
					\item \underline{Integration:} Track peices
					\item \underline{Seperate Testing:} functional/performace
					\item \underline{Packaging:} and releasing the syste
				\end{itemize}
			\item \textbf{3P's:} Processes, Product, People
			\item As the project complexity goes up, the software quality goes down
			\item As the complexity increased, the effort increases

\end{itemize}

\subsection*{X}

\begin{itemize}
		  \item 
\end{itemize}

\end{document}
